Machine Learning based TIR predictor - Methods

### 2020-05-14 methods.tex
Draft for GPUCB description.

    \item \textit{Upper confidence bound (UCB)}. Bandit algorithms \cite{lattimore2018bandit} provide various approaches to sequentially design an where an agent adaptively chooses one or more options among several actions based on certain policies. We consider a type of bandit algorithms, the upper confidence bound algorithm, which is based on the \textit{optimism in the face of uncertainty}. The UCB algorithm, as the name suggested, basically selects RBS sequences with the maximum upper confidence bound, i.e. $\operatorname{argmax}_{\mathbf{x_i \in \mathcal{D}}} \left( \mu_t(\mathbf{x_i}) + \beta_t \sigma_t(\mathbf{x_i})\right)$, where $\beta_T$ is a hyperparmeter balancing the exploitation and exploration, $\mu_t(\mathbf{x}_i), \sigma_t(\matbf{x}_i)$ are the predicted mean and standard deviation at round $t$ for the sequence $\mathbf{x}_i$. 
\end{itemize}

>>>>

    \item \textit{Upper confidence bound (UCB)}. Bandit algorithms \cite{lattimore2018bandit} provide various approaches to sequentially design an where an agent adaptively chooses one or more options among several actions based on certain policies. We consider a type of bandit algorithms, the upper confidence bound algorithm, which is based on the \textit{optimism in the face of uncertainty}. The UCB algorithm, as the name suggested, basically selects RBS sequences with the maximum upper confidence bound, i.e. $\operatorname{argmax}_{\mathbf{x}_i \in \mathcal{D}} \left( \mu_t(\mathbf{x}_i) + \beta_t \sigma_t(\mathbf{x}_i)\right)$,
    where $\beta_t$ is a hyperparmeter balancing the exploitation and exploration, 
    $\mu_t(\mathbf{x}_i), \sigma_t(\mathbf{x}_i)$ are the predicted mean and standard deviation at round $t$ for the sequence $\mathbf{x}_i$. 
\end{itemize}
